manuscript_notes

### 2024-12-10 notes/manuscript_notes.Rmd
update ms-notes and tut-notes
update ms-notes
RR notes

clean up html files (delete old figures, Mention tut 2b priors, ...)

@@

check for timebin, multilevel

>>>>

clean up html files (delete old figures, Mention tut 2b priors line 101, ...)

@@

check for timebin -> time bin

# Rich Dec 10th

## supplementary figures ##

in the main text, change to Supplementary Figure X (as appropriate). 
e.g., page 28, Figure 15 when talking about priors.

## figure 11 ##

very minor point. I would make figure smaller in height. There is a lot of white space and a shorter plot woudl still communicate the main message. 
I would also fatten the point and the lines to make them easier to see.
Add more dodge if necessary.

## conclusion ##

you say

>Statistically controlling for the passage of time during data analysis is equally important as experimental control during the design of an experiment, to better understand human behavior in experimental paradigms.

But I don't think we need it, and I don't understand the second half of the sentence. If we do need it, we need to make it clear what it means.

For now, I deleted it.
